Circumpolar variations in the chaotic nature of Southern Ocean eddy dynamics

### 2022-04-20 revised_paper/revised.tex
final resubmitted version

\graphicspath{ {figures/} }
%\usepackage{lineno,layouts,microtype}

@@

For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member as thin grey lines in Fig.~\ref{Fig:2}(a). 
This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
The observed EKE anomaly \citep[calculated using data from ][ and filtered using the same methods as model output]{Martinez-Moreno2022} indicates that observations are indistinguishable from the individual ensemble members.
Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
Averaged over this wide region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate the variability in the eddy field averaged over the basin.

>>>>

@@

For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member as thin grey lines in Fig.~\ref{Fig:2}(a). 
This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
The observed EKE anomaly \citep[calculated using data from ][ and filtered using the same methods as model output]{Martinez-Moreno2022} indicates that observations are indistinguishable from the individual ensemble members (with the exception of a short period of anomalously low EKE in the early part of the satellite record).
Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
Averaged over this broad region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate the variability in the eddy field averaged over the basin.
